Homework 5

### 2019-10-31 hw5/MSimonsHW5.tex
Correcting problem 1 from hw 5
Correcting number 2 hw 5

\item Assume that if $f(x)$, $g(x)$, $s(x)$, $d(x)$, $p(x)$ in $S[x]$ satisfy
\[
f(x) + g(x) = s(x)
\] \[
f(x) - g(x) = d(x)
\] \[
f(x)g(x) = p(x)
\]
then, for any $\alpha$ in $R$,
\[
\] \[
f(\alpha) + g(\alpha) = s(\alpha)
\] \[
f(\alpha) - g(\alpha) = d(\alpha)
\] \[
f(\alpha)g(\alpha) = p(\alpha)
\]
We can prove that $\phi_{\alpha}$ preserves addition as such:
\[
\phi_{\alpha}(f) + \phi_{\alpha}(g) = f(\alpha) + g(\alpha) = s(\alpha) = \phi_{\alpha}(s)
\] \[
\phi_{\alpha}(f) - \phi_{\alpha}(g) = f(\alpha) - g(\alpha) = d(\alpha) = \phi_{\alpha}(d)
\]
We can prove that $\phi_{\alpha}$ preserves multiplication as such:
\[
\phi_{\alpha}(f)\phi_{\alpha}(g) = f(\alpha)g(\alpha) = p(\alpha) = \phi_{\alpha}(p)
\]
Thus, $\phi_{\alpha}$ is a ring homomorphism.

\item Let $f(\alpha)$, $g(\alpha)$ be elements in $S[\alpha]$.  This implies
that $f(x)$ and $g(x)$ are elements of $S[x]$.  Since $S$ is a ring, its
elements are closed under addition, implying that $S[x]$ preserves
addition as well.  Let $f(x) + g(x) = s(x)$ and $f(x) - g(x) = d(x)$.  Since
$s(x)$ and $d(x)$ are in $S[x]$, $s(\alpha) = f(\alpha) + g(\alpha)$ and
$d(\alpha) = f(\alpha) - g(\alpha)$ are elements of $S[\alpha]$ and $S[\alpha]$
preserves addition.
\\
\\
Similarly, since $S$ preserves multiplication, we can assume $p(x) = f(x)g(x)$
is an element of $S[x]$.  Therefore $p(\alpha) = f(\alpha)g(\alpha)$ is an
element of $S[\alpha]$ and $S[alpha]$ preserves multiplication.
\\
\\
Thus, $S[\alpha]$ is a subring of $R$.

>>>>

\item Assume that if $f(x)$, $g(x)$, $s(x)$, $d(x)$, $p(x)$ in $S[x]$ satisfy
\[
f(x) + g(x) = s(x)
\] \[
f(x) - g(x) = d(x)
\] \[
f(x)g(x) = p(x)
\]
then, for any $\alpha$ in $R$,
\[
\] \[
f(\alpha) + g(\alpha) = s(\alpha)
\] \[
f(\alpha) - g(\alpha) = d(\alpha)
\] \[
f(\alpha)g(\alpha) = p(\alpha)
\]
We can prove that $\varphi_{\alpha}$ preserves addition as such:
\[
\varphi_{\alpha}(f) + \varphi_{\alpha}(g) = f(\alpha) + g(\alpha) = s(\alpha) = \varphi_{\alpha}(s) = \varphi_{\alpha}(f+g)
\]
We can prove that $\varphi_{\alpha}$ preserves multiplication as such:
\[
\varphi_{\alpha}(f)\varphi_{\alpha}(g) = f(\alpha)g(\alpha) = p(\alpha) = \varphi_{\alpha}(p) = \varphi_{\alpha}(fg)
\]
Thus, $\varphi_{\alpha}$ is a ring homomorphism.

\item Let $f(\alpha)$, $g(\alpha)$ be elements in $S[\alpha]$, where
$f(x)$ and $g(x)$ are elements of $S[x]$.
Let $f(x) + g(x) = s(x)$ and $f(x) - g(x) = d(x)$.  Since
$s(x)$ and $d(x)$ are in $S[x]$, $s(\alpha) = f(\alpha) + g(\alpha)$ and
$d(\alpha) = f(\alpha) - g(\alpha)$ are elements of $S[\alpha]$ and $S[\alpha]$
preserves addition and subtraction.
\\
\\
Similarly, since $S$ preserves multiplication, $p(x) = f(x)g(x)$
is an element of $S[x]$.  Therefore $p(\alpha) = f(\alpha)g(\alpha)$ is an
element of $S[\alpha]$ and $S[\alpha]$ preserves multiplication.
\\
\\
Thus, $S[\alpha]$ is a subring of $R$.
